### 2013-02-19 document.tex
Signed-off-by: loopasam <samuel.croset@gmail.com>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Title}
}
% Insert Author names, affiliations and corresponding author email.
\\
Author1$^{1}$, 
Author2$^{2}$, 
Author3$^{3,\ast}$
\\
\bf{1} Author1 Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
\\
$\ast$ E-mail: Corresponding author@institute.edu
\end{flushleft}

@@

@@

@@

pouet pouet blablabalba \cite{Krotzsch2012} for

@@

@@

@@

@@

@@

@@

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{The Functional Therapeutic Chemical Classification System}
}
% Insert Author names, affiliations and corresponding author email.
\\
Samuel Croset$^{1,\ast}$, 
John Overington$^{2}$, 
Dietrich Rebholz-Schuhmann$^{3}$
\\
\bf{1} Samuel Croset Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} John Overington Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Dietrich Rebholz-Schuhmann Dept/Program/Center, Institution Name, City, State, Country
\\
$\ast$ E-mail: Corresponding croset@ebi.ac.uk
\end{flushleft}

@@

The abstract of the paper should be succinct; it must not exceed 300 words. 
Authors should mention the techniques used without going into methodological detail 
and should summarize the most important results. While the abstract is conceptually divided into 
three sections (Background, Methodology/Principal Findings, and Conclusions/Significance), please 
do not apply these distinct headings to the abstract within the article file. Please do 
not include any citations and avoid specialist abbreviations.

@@

We ask that all authors of research articles include a 150–200 word non-technical summary 
of the work as part of the manuscript to immediately follow the abstract. This text is subject to editorial 
change, should be written in the first-person voice, and should be distinct from the scientific abstract. Aim to 
highlight where your work fits within a broader context; present the significance or possible implications of your work 
simply and objectively; and avoid the use of acronyms and complex terminology wherever possible. The goal is to make your 
findings accessible to a wide audience that includes both scientists and non-scientists. Authors may benefit from consulting 
with a science writer or press officer to ensure they effectively communicate their findings to a general audience. Examples 
are available at:

@@

pouet \cite{Krotzsch2012} pouet

The introduction should put the focus of the manuscript into a broader context. 
As you compose the introduction, think of readers who are not experts in this field. 
Include a brief review of the key literature. If there are relevant controversies or disagreements in 
the field, they should be mentioned so that a non-expert reader can delve into these issues further. 
The introduction should conclude with a brief statement of the overall aim of the experiments and a comment 
about whether that aim was achieved.

@@

The results section should provide details of all of the experiments that 
are required to support the conclusions of the paper. There is no specific word limit for 
this section, but details of experiments that are peripheral to the main thrust of the article and that 
detract from the focus of the article should not be included. The section may be divided into subsections, 
each with a concise subheading. Large datasets, including raw data, should be submitted as supporting files; 
these are published online alongside the accepted article. The results section should be written in the past tense.

@@

The discussion should spell out the major conclusions of the work along with some 
explanation or speculation on the significance of these conclusions. How do the 
conclusions affect the existing assumptions and models in the field? How can future research 
build on these observations? What are the key experiments that must be done? The discussion should 
be concise and tightly argued. The results and discussion may be combined into one section, if desired.

@@

This section should provide enough detail for reproduction of the findings. Protocols 
for new methods should be included, but well-established protocols may simply be referenced. While we do 
encourage authors to submit all appendices, detailed protocols, or details of the algorithms for newer or less 
well-established methods, please do so as Supporting Information files. These are not included in the typeset manuscript, 
but are downloadable and fully searchable from the HTML version of the article.

@@

People who contributed to the work but do not fit the criteria for authors should be listed in the 
Acknowledgments, along with their contributions. You must also ensure that anyone named in the Acknowledgments 
agrees to being so named.

Details of the funding sources that have supported the work should be confined to the funding statement 
provided in the online submission system. Do not include them in the Acknowledgments.

@@

The aim of the figure legend should be to describe the key messages of the figure, but 
the figure should also be discussed in the text. An enlarged version of the figure and its full legend 
will often be viewed in a separate window online, and it should be possible for a reader to understand the figure 
without switching back and forth between this window and the relevant parts of the text. Each legend should have 
a concise title of no more than 15 words that can stand alone, without the use of figure part labels. The overall 
legend itself should be succinct, while still explaining all figure parts, symbols and abbreviations. Avoid lengthy descriptions of methods.

@@

Tables should be included at the end of the manuscript file and cited sequentially in the text. 
All tables should have a concise title. Footnotes can be used to explain abbreviations. 
Citations should be indicated using the same style as outlined above. Tables should not occupy more than one 
printed page; larger tables can be published as online supporting information. Tables must be cell-based; 
do not use picture elements, text boxes, tabs, or returns in tables. Please ensure that all tables conform to our 
Guidelines for Figure and Table Preparation when preparing them.
